Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/design.tex
Design

Nail introduces two concepts to handle this, \emph{streams} and \emph{transformations}. 
Streams represent a sequence of bytes that contain some external format. The parsers and generators
that Nail generates always operate on an implicit stream named \cc{\$current} that they process front to
back, reading input or appending output.
Grammars can use the \cc{apply} combinator to parse or generate external data on a different stream,
inserting the result in the data model.

Streams can be defined in two ways.
First, a rule can require streams as arguments, which can be passed in by the program that invokes
the generated parser. Every rule needs to be passed at least the implicit current stream.

Second, the programmer can create temporary streams in the grammar with \emph{transformations},
which are two arbitrary functions called during parsing and output generation respectively.
The parsing function  takes any number of stream arguments and dependent field values,
and produces any number of temporary streams. This function may reposition and read from the
input streams and read the values of dependent fields, but not change their contents and values. 
The generating function has to be an inverse of the parsing function. It takes the same number of
temporary streams that the parsing function produces, and writes the same number of streams and
dependent field values that the parsing function consumes.

>>>>

Nail introduces two concepts to handle these challenges, \emph{streams} and \emph{transformations}. 
Streams represent a sequence of bytes that contain some external format. The parsers and generators
that Nail generates always operate on an implicit stream named \cc{\$current} that they process front to
back, reading input or appending output.
Grammars can use the \cc{apply} combinator to parse or generate external data on a different stream,
inserting the result in the data model.

Streams are passed as arguments to a rule or defined within the grammar through \emph{transformations}.
The current stream is always passed as an implicit parameter.

Transformations are two arbitrary functions called during parsing and output generation.
The parsing function  takes any number of stream arguments and dependent field values,
and produces any number of temporary streams. This function may reposition and read from the
input streams and read the values of dependent fields, but not change their contents and values. 
The generating function has to be an inverse of the parsing function. It takes the same number of
temporary streams that the parsing function produces, and writes the same number of streams and
dependent field values that the parsing function consumes.
